---
title: "dataset-3"
author: "Sunny"
date: "July 20, 2016"
output: html_document
---

```{r packages,echo=FALSE, warning=FALSE, message=FALSE}
setwd("C:/Longitudinal-Project")
#install.packages("crimCV")
library(crimCV)
library(reshape2)
library(dplyr)
#install.packages("mi)
library(mi)
library(ggplot2)
library(gplots)
#install.packages("tigerstats")
library(tigerstats)
library(rgl)
library(car)
```


```{r import, echo=FALSE, warning=FALSE, message=FALSE}
traj_test <- data.frame(read.delim("C:/Longitudinal-Project/isp_dataset_3.txt", stringsAsFactors=FALSE))
names(traj_test)[1:4]=c("ID","Age","gender","class")

strip = function(x){
  res=strsplit(x," ")[[1]][which(strsplit(x," ")[[1]]>2)]
}

traj_test$class = sapply(traj_test[,4],strip)

```

```{r echo=FALSE, warning=FALSE, message=FALSE}
traj_test = mutate(traj_test, class2 = ifelse(class=="asd","asd","typ"))
traj_test = mutate(traj_test, class1 = ifelse(class=="typ",1, ifelse(class=="asd", 2,3)))
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
res_asd_typ = data.frame(matrix(NA, nrow=912, ncol = 8))
names(res_asd_typ)=c("variable","age3", "age6","age9", "age12","age18","age24","age36")
age_list=sort(unique(traj_test$Age))
i = 1
for(var in names(traj_test)[5:916]){
  test_set = subset(traj_test[,c("Age","class",var)],class != "hra")
  res_asd_typ[i,1]=var
  for(age in unique(test_set$Age)){
    test_age = subset(test_set,Age==age)
    tt = t.test(subset(test_age,class=="asd")[,3],subset(test_age,class=="typ")[,3])
    res_asd_typ[i,which(age_list==age)+1]=tt$p.value
  }
  i = i+1
}
res_asd_typ_bin=res_asd_typ
for(col in c(2:8)){
  res_asd_typ_bin[,col]=ifelse(res_asd_typ_bin[,col]>=0.05,0,1)
}
```

Number of variables that have significant average difference between `asd` and `typ` for at least one time point:  

```{r echo=FALSE, warning=FALSE, message=FALSE}
res_asd_typ_bin$age3t12 = apply(res_asd_typ_bin[2:5],1,sum)
res_asd_typ_bin_sub=subset(res_asd_typ_bin,age3t12==4)
res_asd_typ_bin$age3t36 = apply(res_asd_typ_bin[2:8],1,sum)
res_asd_typ_3t36=subset(res_asd_typ_bin,age3t36>=1)
dim(res_asd_typ_bin_sub)
dim(res_asd_typ_3t36)
#res_asd_typ_3t36
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
res_asd_hra = data.frame(matrix(NA, nrow=912, ncol = 8))
names(res_asd_hra)=c("variable","age3", "age6","age9", "age12","age18","age24","age36")
age_list=sort(unique(traj_test$Age))
i = 1
for(var in names(traj_test)[5:916]){
  test_set = subset(traj_test[,c("Age","class",var)],class != "typ")
  res_asd_hra[i,1]=var
  for(age in unique(test_set$Age)){
    test_age = subset(test_set,Age==age)
    tt = t.test(subset(test_age,class=="asd")[,3],subset(test_age,class=="hra")[,3])
    res_asd_hra[i,which(age_list==age)+1]=tt$p.value
  }
  i = i+1
}
res_asd_hra_bin=res_asd_hra
for(col in c(2:8)){
  res_asd_hra_bin[,col]=ifelse(res_asd_hra_bin[,col]>=0.05,0,1)
}
```

Number of variables that have significant average difference between `asd` and `hra` for at least one time point over age 3 - 36 month:  

```{r echo=FALSE, warning=FALSE, message=FALSE}
res_asd_hra_bin$age3t12 = apply(res_asd_hra_bin[2:5],1,sum)
res_asd_hra_bin_sub=subset(res_asd_hra_bin,age3t12==4)
res_asd_hra_bin$age3t36 = apply(res_asd_hra_bin[2:8],1,sum)
res_asd_hra_3t36=subset(res_asd_hra_bin,age3t36>=1)
dim(res_asd_hra_bin_sub)
dim(res_asd_hra_3t36)
#res_asd_hra_3t36
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
res_typ_hra = data.frame(matrix(NA, nrow=912, ncol = 8))
names(res_typ_hra)=c("variable","age3", "age6","age9", "age12","age18","age24","age36")
age_list=sort(unique(traj_test$Age))
i = 1
for(var in names(traj_test)[5:916]){
  test_set = subset(traj_test[,c("Age","class",var)],class != "asd")
  res_typ_hra[i,1]=var
  for(age in unique(test_set$Age)){
    test_age = subset(test_set,Age==age)
    tt = t.test(subset(test_age,class=="typ")[,3],subset(test_age,class=="hra")[,3])
    res_typ_hra[i,which(age_list==age)+1]=tt$p.value
  }
  i = i+1
}
res_typ_hra_bin=res_typ_hra
for(col in c(2:8)){
  res_typ_hra_bin[,col]=ifelse(res_typ_hra_bin[,col]>=0.05,0,1)
}
```

Number of variables that have significant average difference between `typ` and `hra` for at least one time point:  

```{r echo=FALSE, warning=FALSE, message=FALSE}
res_typ_hra_bin$age3t12 = apply(res_typ_hra_bin[2:5],1,sum)
res_typ_hra_bin_sub=subset(res_typ_hra_bin,age3t12==4)
res_typ_hra_bin$age3t36 = apply(res_typ_hra_bin[2:8],1,sum)
res_typ_hra_3t36=subset(res_typ_hra_bin,age3t36>=1)
dim(res_typ_hra_bin_sub)
dim(res_typ_hra_3t36)
#res_typ_hra_3t36
```

Intersection of the signficant variables
```
significantly different between **asd** and **typ** for at least one time point   
significantly different between **asd** and **hra** for at least one time point  
significantly different between **typ** and **hra** for at least one time point   
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
intersect(res_typ_hra_3t36$variable,intersect(res_asd_hra_3t36$variable,res_asd_typ_3t36$variable))
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
g = ggplot(data=traj_test,aes(x = Age, y = C3.SampE.s0) )
g+geom_point(aes(color=class))+geom_smooth(aes(group=class, color=class))
#g+geom_point(aes(color=class2))+geom_smooth(aes(group=class2, color=class2))
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
g = ggplot(data=traj_test,aes(x = Age, y = O1.SampE.s0) )
g+geom_point(aes(color=class))+geom_smooth(aes(group=class, color=class))
#g+geom_point(aes(color=class2))+geom_smooth(aes(group=class2, color=class2))
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
g = ggplot(data=traj_test,aes(x = Age, y = F7.SampE.s0) )
g+geom_point(aes(color=class))+geom_smooth(aes(group=class, color=class))
#g+geom_point(aes(color=class2))+geom_smooth(aes(group=class2, color=class2))
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
g = ggplot(data=traj_test,aes(x = Age, y = Pz.SampE.s0) )
g+geom_point(aes(color=class))+geom_smooth(aes(group=class, color=class))
#g+geom_point(aes(color=class2))+geom_smooth(aes(group=class2, color=class2))
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
g = ggplot(data=traj_test,aes(x = Age, y = P7.SampE.s0) )
g+geom_point(aes(color=class))+geom_smooth(aes(group=class, color=class))
#g+geom_point(aes(color=class2))+geom_smooth(aes(group=class2, color=class2))
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
g = ggplot(data=traj_test,aes(x = Age, y = C3.RR.s0) )
g+geom_point(aes(color=class))+geom_smooth(aes(group=class, color=class))
#g+geom_point(aes(color=class2))+geom_smooth(aes(group=class2, color=class2))
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
g = ggplot(data=traj_test,aes(x = Age, y = O1.RR.s0) )
g+geom_point(aes(color=class))+geom_smooth(aes(group=class, color=class))
#g+geom_point(aes(color=class2))+geom_smooth(aes(group=class2, color=class2))
#ggsave("C:/Longitudinal-Project/plots/C3_sampE_s2.jpeg", width=35, height=30, units = "cm")
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
g = ggplot(data=traj_test,aes(x = Age, y = F4.RR.s0) )
g+geom_point(aes(color=class))+geom_smooth(aes(group=class, color=class))
#g+geom_point(aes(color=class2))+geom_smooth(aes(group=class2, color=class2))
#ggsave("C:/Longitudinal-Project/plots/C3_sampE_s2.jpeg", width=35, height=30, units = "cm")
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
g = ggplot(data=traj_test,aes(x = Age, y = F8.RR.s0) )
g+geom_point(aes(color=class))+geom_smooth(aes(group=class, color=class))
#g+geom_point(aes(color=class2))+geom_smooth(aes(group=class2, color=class2))
#ggsave("C:/Longitudinal-Project/plots/C3_sampE_s2.jpeg", width=35, height=30, units = "cm")
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
g = ggplot(data=traj_test,aes(x = Age, y = Fp2.RR.s0) )
g+geom_point(aes(color=class))+geom_smooth(aes(group=class, color=class))
#g+geom_point(aes(color=class2))+geom_smooth(aes(group=class2, color=class2))
#ggsave("C:/Longitudinal-Project/plots/C3_sampE_s2.jpeg", width=35, height=30, units = "cm")
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
g = ggplot(data=traj_test,aes(x = Age, y = P3.RR.s0) )
g+geom_point(aes(color=class))+geom_smooth(aes(group=class, color=class))
#g+geom_point(aes(color=class2))+geom_smooth(aes(group=class2, color=class2))
#ggsave("C:/Longitudinal-Project/plots/C3_sampE_s2.jpeg", width=35, height=30, units = "cm")
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
g = ggplot(data=traj_test,aes(x = Age, y = Pz.RR.s0) )
g+geom_point(aes(color=class))+geom_smooth(aes(group=class, color=class))
#g+geom_point(aes(color=class2))+geom_smooth(aes(group=class2, color=class2))
#ggsave("C:/Longitudinal-Project/plots/C3_sampE_s2.jpeg", width=35, height=30, units = "cm")
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
g = ggplot(data=traj_test,aes(x = Age, y = T8.RR.s0) )
g+geom_point(aes(color=class))+geom_smooth(aes(group=class, color=class))
#g+geom_point(aes(color=class2))+geom_smooth(aes(group=class2, color=class2))
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
g = ggplot(data=traj_test,aes(x = Age, y = P7.RR.s0) )
g+geom_point(aes(color=class))+geom_smooth(aes(group=class, color=class))
#g+geom_point(aes(color=class2))+geom_smooth(aes(group=class2, color=class2))
#ggsave("C:/Longitudinal-Project/plots/C3_sampE_s2.jpeg", width=35, height=30, units = "cm")
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
g = ggplot(data=traj_test,aes(x = Age, y = O1.DET.s0) )
g+geom_point(aes(color=class))+geom_smooth(aes(group=class, color=class))
#g+geom_point(aes(color=class2))+geom_smooth(aes(group=class2, color=class2))
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
g = ggplot(data=traj_test,aes(x = Age, y = O2.DET.s0) )
g+geom_point(aes(color=class))+geom_smooth(aes(group=class, color=class))
#g+geom_point(aes(color=class2))+geom_smooth(aes(group=class2, color=class2))
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
g = ggplot(data=traj_test,aes(x = Age, y = F7.DET.s0) )
g+geom_point(aes(color=class))+geom_smooth(aes(group=class, color=class))
#g+geom_point(aes(color=class2))+geom_smooth(aes(group=class2, color=class2))
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
g = ggplot(data=traj_test,aes(x = Age, y = F8.DET.s0) )
g+geom_point(aes(color=class))+geom_smooth(aes(group=class, color=class))
#g+geom_point(aes(color=class2))+geom_smooth(aes(group=class2, color=class2))
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
g = ggplot(data=traj_test,aes(x = Age, y = Pz.DET.s0) )
g+geom_point(aes(color=class))+geom_smooth(aes(group=class, color=class))
#g+geom_point(aes(color=class2))+geom_smooth(aes(group=class2, color=class2))
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
g = ggplot(data=traj_test,aes(x = Age, y = T8.DET.s0) )
g+geom_point(aes(color=class))+geom_smooth(aes(group=class, color=class))
#g+geom_point(aes(color=class2))+geom_smooth(aes(group=class2, color=class2))
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
g = ggplot(data=traj_test,aes(x = Age, y = P7.DET.s0) )
g+geom_point(aes(color=class))+geom_smooth(aes(group=class, color=class))
#g+geom_point(aes(color=class2))+geom_smooth(aes(group=class2, color=class2))
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
g = ggplot(data=traj_test,aes(x = Age, y = O1.LAM.s0) )
g+geom_point(aes(color=class))+geom_smooth(aes(group=class, color=class))
#g+geom_point(aes(color=class2))+geom_smooth(aes(group=class2, color=class2))
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
g = ggplot(data=traj_test,aes(x = Age, y = F7.LAM.s0) )
g+geom_point(aes(color=class))+geom_smooth(aes(group=class, color=class))
#g+geom_point(aes(color=class2))+geom_smooth(aes(group=class2, color=class2))
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
g = ggplot(data=traj_test,aes(x = Age, y = P7.LAM.s0) )
g+geom_point(aes(color=class))+geom_smooth(aes(group=class, color=class))
#g+geom_point(aes(color=class2))+geom_smooth(aes(group=class2, color=class2))
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
g = ggplot(data=traj_test,aes(x = Age, y = C3.L_entr.s0) )
g+geom_point(aes(color=class))+geom_smooth(aes(group=class, color=class))
#g+geom_point(aes(color=class2))+geom_smooth(aes(group=class2, color=class2))
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
g = ggplot(data=traj_test,aes(x = Age, y = C4.L_entr.s0) )
g+geom_point(aes(color=class))+geom_smooth(aes(group=class, color=class))
#g+geom_point(aes(color=class2))+geom_smooth(aes(group=class2, color=class2))
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
g = ggplot(data=traj_test,aes(x = Age, y = O1.L_entr.s0) )
g+geom_point(aes(color=class))+geom_smooth(aes(group=class, color=class))
#g+geom_point(aes(color=class2))+geom_smooth(aes(group=class2, color=class2))
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
g = ggplot(data=traj_test,aes(x = Age, y = F8.L_entr.s0) )
g+geom_point(aes(color=class))+geom_smooth(aes(group=class, color=class))
#g+geom_point(aes(color=class2))+geom_smooth(aes(group=class2, color=class2))
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
g = ggplot(data=traj_test,aes(x = Age, y = Pz.L_entr.s0) )
g+geom_point(aes(color=class))+geom_smooth(aes(group=class, color=class))
#g+geom_point(aes(color=class2))+geom_smooth(aes(group=class2, color=class2))
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
g = ggplot(data=traj_test,aes(x = Age, y = P7.L_entr.s0) )
g+geom_point(aes(color=class))+geom_smooth(aes(group=class, color=class))
#g+geom_point(aes(color=class2))+geom_smooth(aes(group=class2, color=class2))
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
g = ggplot(data=traj_test,aes(x = Age, y = C4.L_max.s0) )
g+geom_point(aes(color=class))+geom_smooth(aes(group=class, color=class))
#g+geom_point(aes(color=class2))+geom_smooth(aes(group=class2, color=class2))
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
g = ggplot(data=traj_test,aes(x = Age, y = O2.L_max.s0) )
g+geom_point(aes(color=class))+geom_smooth(aes(group=class, color=class))
#g+geom_point(aes(color=class2))+geom_smooth(aes(group=class2, color=class2))
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
g = ggplot(data=traj_test,aes(x = Age, y = F3.L_max.s0) )
g+geom_point(aes(color=class))+geom_smooth(aes(group=class, color=class))
#g+geom_point(aes(color=class2))+geom_smooth(aes(group=class2, color=class2))
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
g = ggplot(data=traj_test,aes(x = Age, y = F7.L_max.s0) )
g+geom_point(aes(color=class))+geom_smooth(aes(group=class, color=class))
#g+geom_point(aes(color=class2))+geom_smooth(aes(group=class2, color=class2))
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
g = ggplot(data=traj_test,aes(x = Age, y = F8.L_mean.s0) )
g+geom_point(aes(color=class))+geom_smooth(aes(group=class, color=class))
#g+geom_point(aes(color=class2))+geom_smooth(aes(group=class2, color=class2))
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
g = ggplot(data=traj_test,aes(x = Age, y = F8.L_mean.s1) )
g+geom_point(aes(color=class))+geom_smooth(aes(group=class, color=class))
#g+geom_point(aes(color=class2))+geom_smooth(aes(group=class2, color=class2))
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
g = ggplot(data=traj_test,aes(x = Age, y = F4.TT.s3) )
g+geom_point(aes(color=class))+geom_smooth(aes(group=class, color=class))
#g+geom_point(aes(color=class2))+geom_smooth(aes(group=class2, color=class2))
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
g = ggplot(data=traj_test,aes(x = Age, y = Fp2.L_entr.s4) )
g+geom_point(aes(color=class))+geom_smooth(aes(group=class, color=class))
#g+geom_point(aes(color=class2))+geom_smooth(aes(group=class2, color=class2))
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
g = ggplot(data=traj_test,aes(x = Age, y = F3.TT.s4) )
g+geom_point(aes(color=class))+geom_smooth(aes(group=class, color=class))
#g+geom_point(aes(color=class2))+geom_smooth(aes(group=class2, color=class2))
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
c3sampes2_typ = polyfitGC(C3.SampE.s2~Age, data = traj_test%>%filter(class2=="typ"),degree = 4)
c3sampes2_asd = polyfitGC(C3.SampE.s2~Age, data = traj_test%>%filter(class2=="asd"),degree = 4)
plot(c3sampes2_asd)
plot(c3sampes2_typ)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
